Oregon distributed lag model best fit degree of freedom

### 2017-11-14 r_scripts/analysis/model_dl_spline_knots.Rmd

# fill outcome name in first column
fit_mat[,1] <- "Beta - 2 agonists"
# fill in exposure (geo smoke)
fit_mat[,2] <- "geo_smk10"
# fit type
fit_mat[,3] <- "ns"

@@

@@

kable(fit_mat, caption="Distributed lag spline of 3-6 degree of freedom fit by AIC")

lag_spline_best_fit <- as_tibble(fit_mat) %>%  
  slice(which.min(aic)) # df of 3 has the smallest AIC

# kable
knitr::kable(lag_spline_best_fit, caption = paste0("Distributed lag spline ",
  "degree of freedom best fit by AIC"))
```

>>>>

# fill outcome name in first column
fit_mat[,1] <- "SABA"
# fill in exposure (geo smoke)
fit_mat[,2] <- "geo_smk10"
# fit type
fit_mat[,3] <- "ns"

@@

fit_mat_saba <- as_data_frame(fit_mat)

@@

# kable(fit_mat, caption="Distributed lag spline of 3-6 degree of freedom fit by AIC")

# lag_spline_best_fit <- as_tibble(fit_mat) %>%  
#   slice(which.min(aic)) # df of 3 has the smallest AIC

# kable
# knitr::kable(lag_spline_best_fit, caption = paste0("Distributed lag spline ",
#   "degree of freedom best fit by AIC"))
```

```{r diseases, message=FALSE, echo=FALSE, warning=FALSE}
var_list <- c('respiratory', 'asthma', 'pneumonia',  'acute_bronch', 'copd', 
              'cvd', 'isch_heart_dis', 'arrhythmia', 'heart_failure', 
              'cerbrovas_dis', 'myocardial_infarc', 'broken_arm')

datalist <- list()

  # j <- c('respiratory')

  # standard for statement without parallel computing
  for(j in var_list){
  read_path <- paste('../data_new/casecrossover/time_strat/or', j, 'may_to_sep_time_strat_casecross.csv', sep='_')
  or_disease <- read_csv(read_path)

  or_disease_df <- data.frame(or_disease)

  or_disease_lag_df <- or_disease_df %>%
  left_join(or_zip_to_county, by = "ZIPCODE") %>%
  left_join(or_pop, by = "county") %>%
  mutate(day = ifelse(weekdays(date) == "Monday" |
                      weekdays(date) == "Tuesday" |
                      weekdays(date) == "Wednesday"|
                      weekdays(date) == "Thursday"|
                      weekdays(date) == "Friday", "weekday",
               ifelse(weekdays(date) == "Saturday" |
                      weekdays(date) == "Sunday", "weekend", NA))) %>%
  mutate(geo_smk_pm10_zip = geo_smk_pm_zip/10,
         geo_smk_pm10_lag1_zip =geo_smk_pm_lag1_zip/10,
         geo_smk_pm10_lag2_zip =geo_smk_pm_lag2_zip/10,
         geo_smk_pm10_lag3_zip =geo_smk_pm_lag3_zip/10,
         geo_smk_pm10_lag4_zip =geo_smk_pm_lag4_zip/10,
         geo_smk_pm10_lag5_zip =geo_smk_pm_lag5_zip/10,
         geo_smk_pm10_lag6_zip =geo_smk_pm_lag6_zip/10,
         geo_smk_pm10_lag7_zip =geo_smk_pm_lag7_zip/10)

or_disease_lag_df$day[which(or_disease_lag_df$date=="2013-05-27")] <- "weekend"
or_disease_lag_df$day[which(or_disease_lag_df$date=="2013-07-04")] <- "weekend"
or_disease_lag_df$day[which(or_disease_lag_df$date=="2013-09-02")] <- "weekend"

# which(colnames(or_disease_lag_df)=="geo_smk_pm10_zip") #174
# which(colnames(or_disease_lag_df)=="geo_smk_pm10_lag1_zip") #175
# which(colnames(or_disease_lag_df)=="wrf_temp_zip") #94
# which(colnames(or_disease_lag_df)=="wrf_temp_lag1_zip") #151

or_disease_geo_lag <- or_disease_lag_df %>%
  select(174, 175:181) # GWR-method

or_disease_temp_lag <- or_disease_lag_df %>%
  select(94, 151:157) # GWR-method

lag_max <- 7

or_disease_geo_lag <- as.matrix(or_disease_geo_lag)
or_disease_temp_lag <- as.matrix(or_disease_temp_lag)

# fill outcome name in first column
fit_mat[,1] <- j
# fill in exposure (geo smoke)
fit_mat[,2] <- "geo_smk10"
# fit type
fit_mat[,3] <- "ns"

    # multiply lagged pm matrix by basis
    or_disease_geo_lag_B <- or_disease_geo_lag%*%B
    or_disease_temp_lag_B <- or_disease_temp_lag%*%B

    fit <- clogit(outcome ~ or_disease_geo_lag_B + or_disease_temp_lag_B + strata(personkey), 
              or_disease_lag_df)

    } # end model fit loop
i <- match(j, var_list)
datalist[[i]] <- as_data_frame(fit_mat)
  }

combine <- bind_rows(datalist)

combine_saba <- bind_rows(fit_mat_saba, combine)

kable(combine_saba, caption="Distributed lag spline of 3-6 degree of freedom fit by AIC")

write_path <- paste0('../data_new/medication/model_dl_spline_knots.csv')
write_csv(combine_saba, write_path)
